Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-19 oldSections/edhocProtocol.tex
[fix] moved old sources to separate dir to avoid confusion

% !TEX root = journal-version.tex
In this section, we describe the various key establishment methods of the \mEdhoc{} protocol.
%
Following~\cite{Norr21}, we refer to the two roles executing the protocol as the initiator $I$ and the responder $R$.
%
We annotate values with $I$ and $R$ to make explicit which role they belong to.
%

We denote by $\langle d_{t, \mathit{id}}, Q_{t, \mathit{id}}\rangle$ public-private key pairs, where $d$ is the private key, $Q$ is the public key, $t \in \{e, s\}$ indicates whether the key is ephemeral or static, and $\mathit{id}$ indicates the party to whom the key pair belongs.
%
When clear from context, we will often drop part (or all) of the subscript.
%
Static key pairs (suitable for both regular and challenge-response signatures) are long-term authentication credentials, while ephemeral key pairs are those which are generated afresh for each instantiation of the protocol.
%

Parties can authenticate using regular signatures or challenge-response signatures. 
%
In the former case, we say that they use the \emph{signature based authentication method} (\mSig{}).
%
In the latter, we say, following the terminology in the \mSpec{}, that they use the \emph{static key authentication method} (\mStat{}).
%
For more details about the challenge-response terminology, see~\cite{DBLP:conf/crypto/Krawczyk05}.

%%------------------------------------------------------------------------- sub
%

>>>>

% !TEX root = journal-version.tex

We now present the structure of the protocol using notation for key material,
elliptic curve operations and
identities mostly adopted from NIST SP 800-56A Rev. 3~\cite{sp800-56a-rev3}.
%
One notable difference is that we refer to the two roles executing the protocol
as the initiator $I$ and the responder $R$.
%
We do this to avoid confusing roles with the parties taking them on.
%
Values in the analysis are subscripted with $I$ and $R$ when necessary to
distinguish which role is associated with the values.
%

%------------------------------------------------------------------------- sub
\subsection{Preliminaries}
\label{sec:preliminaries}
Private/public key pairs are written
$\langle d_{t,\mathit{id}},\,Q_{t,\mathit{id}}\rangle$,
where $d$ is the private key, $Q$ the public key, $t \in \{e, s\}$ denotes
whether the key is ephemeral or static, and $\mathit{id}$ is the role or
party controlling the key pair.
%
When irrelevant, we drop the subscript or parts thereof.
%
Ephemeral key pairs are generated fresh for each instantiation of the protocol
and static key pairs are long-term keys used for authentication.
%
Static key pairs are suitable for either regular signatures or
challenge-response signatures.
%
When a party uses regular signatures for authentication, we say that they use
the \emph{signature based authentication method}, or \mSig{} for short.
%
When a party uses challenge-response signatures for authentication, we say that
they use the \emph{static key authentication method}, or \mStat{} for short.
%
The latter naming may appear confusing since signature keys are equally static,
but is chosen to make the connection to the \mSpec{} clear.
%
We adopt the challenge-response terminology for this style of authentication
from~\cite{DBLP:conf/crypto/Krawczyk05}.
%
